A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-03-19 paper/paper.tex
paper: minor polish
reformulating conclusion

Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore. For instance, it produces figure \ref{fig:intuition} for $n=2$ and $\nu=2$.

@@

By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~\cite{altenkirch15}, we expect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\cite{bezem13,cohen16,angiuli21}. A key point is that, thanks to the indexed approach, we expect univalence to hold by definition. If these intuitions are correct, this would definitively root cubical type theory on top of iterated parametricity translation.

>>>>

Note that for a fixed constant $n$, the coherence conditions evaluate to a reflexivity proof, so that the construction evaluates to an effective sequence of types of iterated relations not mentioning them anymore. For instance, it produces Fig.~\ref{fig:intuition} for $n=2$ and $\nu=2$.

@@

By equipping the universe construction with a structure of equivalences, as suggested along the lines of Altenkirch and Kaposi~\cite{altenkirch15}, we expect the construction to be able to serve as a basis for syntactic models of various versions of cubical type theory~\cite{bezem13,cohen16,angiuli21}, saving the detour via the fibered approach inherent to usual presheaf models. This would a priori preserve definitional properties which may be lost when detouring via presheaves. In particular, we conjecture being able to justify univalence holding definitionally. Our approach would also definitively ground cubical type theory in iterated parametricity.
